2040 greenhouse gas reduction targets

### 2023-06-22 paperCharts.Rmd
additional paper numbers and target charts

@@

@@

CDR <- data.frame(
  result=c("CCS_deployment_in_2030_MtCO2","CCS_deployment_in_2040_MtCO2","CCS_upscaling_rates_2030_2040_%","novel_CDR_upscaling_rates_2030_2040_%","novel_CDR_deployment_in_2040_MtCO2"),
  reference_value=c(
    round(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
    round(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
    round(rateCCS %>% filter(scenario == mainScen) %>% pull(rate)*100),
    round(rateCDR %>% filter(scenario == mainScen) %>% pull(rate)*100),
    round(totalCDR %>% filter(period == 2040, scenario == mainScen) %>% pull(value))
  ),
  min = c(
    round(min(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(min(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(min(rateCCS %>% pull(rate))*100),
    round(min(rateCDR %>% pull(rate))*100),
    round(min(totalCDR %>% pull(value)))
  ),
  max = c(
    round(max(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(max(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(max(rateCCS %>% pull(rate))*100),
    round(max(rateCDR %>% pull(rate))*100),
    round(max(totalCDR %>% pull(value)))
  )
)

@@

vars <- c(
  "Hydrogen"="FE|Hydrogen",
  "Gases"="FE|Gases"
)

@@

@@

g[["Emissions reductions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Emissions\nreductions", y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)

@@

g[["Energy savings"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Final Energy\nDemand", y = 750, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Final Energy\nDemand", y = 787, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.7, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(400,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.2, na.rm = TRUE)

@@

g[["Renewables Share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.5, color = "black", alpha = 0.5) +
  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)

#

@@

#target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
g[["Solar photovoltaics"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Solar\nphotovoltaics", y = 600, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.3, na.rm = TRUE)

>>>>

indirect_electrification <- data.frame(
  indirect_electrification_EJ = c("total","buildings","transport","industry"),
  reference_value=c(
    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Hydrogen","FE|Gases|Hydrogen","FE|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Buildings|Hydrogen","FE|Buildings|Gases|Hydrogen","FE|Buildings|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Transport|Hydrogen","FE|Transport|Gases|Hydrogen","FE|Transport|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1),
    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Industry|Hydrogen","FE|Industry|Gases|Hydrogen","FE|Industry|Liquids|Hydrogen"), scenario == mainScen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value),1)
  ),
  min=c(
    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Hydrogen","FE|Gases|Hydrogen","FE|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Buildings|Hydrogen","FE|Buildings|Gases|Hydrogen","FE|Buildings|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Transport|Hydrogen","FE|Transport|Gases|Hydrogen","FE|Transport|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Industry|Hydrogen","FE|Industry|Gases|Hydrogen","FE|Industry|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1)
  ),
  max=c(
    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Hydrogen","FE|Gases|Hydrogen","FE|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Buildings|Hydrogen","FE|Buildings|Gases|Hydrogen","FE|Buildings|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Transport|Hydrogen","FE|Transport|Gases|Hydrogen","FE|Transport|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1),
    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("FE|Industry|Hydrogen","FE|Industry|Gases|Hydrogen","FE|Industry|Liquids|Hydrogen"), tgt2030 %in% tgt2030Scen) %>% group_by(scenario,tgt2030) %>% summarize(value = sum(value),.groups = "keep") %>% pull(value)),1)
  )
)

electricity_demand_increase <- left_join(
  df %>%
  filter(region == "EU27", period %in% c(2030,2040), variable %in% c("FE|Electricity"), tgt2050 != "Npi")
  ,
  df %>%
  filter(region == "EU27", period == 2020, variable %in% c("FE|Electricity"), tgt2050 != "Npi") %>%
  mutate(base = value,.groups = "keep") %>%
  select(scenario,base)
  , by = join_by(scenario == scenario)
) %>%
  mutate(upscale = value/base)

electricity_demand_upscale <- data.frame(
  wind_and_Solar_gen_upscale=c("2030","2040"),
  reference_value=c(
    round(electricity_demand_increase %>% filter(scenario == mainScen, period == "2030") %>% pull(upscale)*100),
    round(electricity_demand_increase %>% filter(scenario == mainScen, period == "2040") %>% pull(upscale)*100)
    ),
  min = c(
   round(min(electricity_demand_increase %>% filter(tgt2030 %in% tgt2030Scen, period == "2030") %>% pull(upscale)*100)),
   round(min(electricity_demand_increase %>% filter(tgt2030 %in% tgt2030Scen, period == "2040") %>% pull(upscale)*100))
   ),
  max = c(
   round(max(electricity_demand_increase %>% filter(tgt2030 %in% tgt2030Scen, period == "2030") %>% pull(upscale)*100)),
   round(max(electricity_demand_increase %>% filter(tgt2030 %in% tgt2030Scen, period == "2040") %>% pull(upscale)*100))
   )
)

electricity_share_in_FE <- data.frame(
  electricity_share_in_FE = c("2040"),
  reference_value=c(
    round(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), scenario == mainScen) %>% pull(value)*100)
  ),
  min=c(
    round(min(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
  ),
  max=c(
    round(max(df %>% filter(region == "EU27", period == 2040, variable %in% c("Final Energy|Electricity Share"), tgt2030 %in% tgt2030Scen, tgt2050 != "Npi") %>% pull(value)*100))
  )
)

wind_and_Solar_gen_upscale <- left_join(
  df %>%
  filter(region == "EU27", period %in% c(2030,2040), variable %in% c("SE|Electricity|Wind|Offshore", "SE|Electricity|Wind|Onshore", "SE|Electricity|Solar|PV", "SE|Electricity|Solar|CSP"), tgt2050 != "Npi") %>%
  group_by(scenario,tgt2030,period) %>%
  summarize(value = sum(value),.groups = "keep")
  ,
  df %>%
  filter(region == "EU27", period == 2020, variable %in% c("SE|Electricity|Wind|Offshore", "SE|Electricity|Wind|Onshore", "SE|Electricity|Solar|PV", "SE|Electricity|Solar|CSP"), tgt2050 != "Npi") %>%
  group_by(scenario,tgt2030) %>%
  summarize(base = sum(value),.groups = "keep")
  , by = join_by(scenario == scenario, tgt2030 == tgt2030)
) %>%
  mutate(upscale = value/base)

gen_upscale <- data.frame(
  wind_and_Solar_gen_upscale=c("2030","2040"),
  reference_value=c(
    round(wind_and_Solar_gen_upscale %>% filter(scenario == mainScen, period == "2030") %>% pull(upscale),1),
    round(wind_and_Solar_gen_upscale %>% filter(scenario == mainScen, period == "2040") %>% pull(upscale),1)
    ),
  min = c(
   round(min(wind_and_Solar_gen_upscale %>% filter(tgt2030 %in% tgt2030Scen, period == "2030") %>% pull(upscale)),1),
   round(min(wind_and_Solar_gen_upscale %>% filter(tgt2030 %in% tgt2030Scen, period == "2040") %>% pull(upscale)),1)
   ),
  max = c(
   round(max(wind_and_Solar_gen_upscale %>% filter(tgt2030 %in% tgt2030Scen, period == "2030") %>% pull(upscale)),1),
   round(max(wind_and_Solar_gen_upscale %>% filter(tgt2030 %in% tgt2030Scen, period == "2040") %>% pull(upscale)),1)
   )
)

@@

indirect_electrification %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

electricity_demand_upscale %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

electricity_share_in_FE %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

gen_upscale %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

CDR <- data.frame(
  result=c("CCS_deployment_in_2030_MtCO2","CCS_deployment_in_2040_MtCO2","CCS_upscaling_rates_2030_2040_%","novel_CDR_upscaling_rates_2030_2040_%","novel_CDR_deployment_in_2040_MtCO2"),
  reference_value=c(
    round(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
    round(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", scenario == mainScen) %>% pull(value)),
    round((rateCCS %>% filter(scenario == mainScen) %>% pull(rate)-1)*100),
    round((rateCDR %>% filter(scenario == mainScen) %>% pull(rate)-1)*100),
    round(totalCDR %>% filter(period == 2040, scenario == mainScen) %>% pull(value))
  ),
  min = c(
    round(min(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(min(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round((min(rateCCS %>% pull(rate))-1)*100),
    round((min(rateCDR %>% pull(rate))-1)*100),
    round(min(totalCDR %>% pull(value)))
  ),
  max = c(
    round(max(df %>% filter(region == "EU27", period == 2030, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round(max(df %>% filter(region == "EU27", period == 2040, variable == "Carbon Management|Storage", tgt2030 %in% tgt2030Scen) %>% pull(value))),
    round((max(rateCCS %>% pull(rate))-1)*100),
    round((max(rateCDR %>% pull(rate))-1)*100),
    round(max(totalCDR %>% pull(value)))
  )
)

@@

vars <- c(
  "Hydrogen"="FE|Hydrogen",
  "Gases"="FE|Gases"
  #"Syngas" = "FE|Gases|Hydrogen",
  #"Biogas" = "FE|Gases|Biomass",
  #"Natural gas" = "FE|Gases|Fossil"
)

plotData <- df %>% 
  filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars), tgt2050 != "Npi") %>% 
  mutate(variable = factor(variable, levels=vars))  %>% 
  group_by(model,scenario,region,period) %>% 
  mutate(cumsum = cumsum(value),
         sum = sum(value)) %>% 
  group_by(model,region,variable,period) %>% 
  mutate(ribbon.max=max(cumsum),
         ribbon.min=min(cumsum)) %>% 
  group_by(model,region,period) %>% 
  mutate(ribbon.max.total=max(sum),
         ribbon.min.total=min(sum))

@@

# vars <- c(
#   "Hydrogen"="FE|Hydrogen",
#   #"Gases"="FE|Gases"
#   "Syngas" = "FE|Gases|Hydrogen",
#   "Biogas" = "FE|Gases|Biomass",
#   "Natural gas" = "FE|Gases|Fossil"
# )
# 
# plotData <- df %>% 
#   filter(region == "EU27", period %in% c(2020,2030,2040,2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars), tgt2050 != "Npi") %>% 
#   mutate(variable = factor(variable, levels=vars))  %>% 
#   group_by(model,scenario,region,period,bioLim) %>% 
#   mutate(cumsum = cumsum(value),
#          sum = sum(value)) %>% 
#   group_by(model,region,variable,period,bioLim) %>% 
#   mutate(ribbon.max=max(cumsum),
#          ribbon.min=min(cumsum)) %>% 
#   group_by(model,region,period) %>% 
#   mutate(ribbon.max.total=max(sum),
#          ribbon.min.total=min(sum))
# 
#   
# g[["FE Gases"]] <- 
#   ggplot(plotData,aes(x=period,y=value)) +
#   geom_col(data=plotData %>% filter(scenario %in% c(mainScen,"Nzero_55_bio12")), aes(fill = variable, alpha=factor(period))) +
#   #geom_errorbar(data=plotData %>% filter(period != 2020), aes(ymin=ribbon.min, ymax=ribbon.max, group=variable), width=8, colour="black", alpha=0.9, size=1,position = position_dodge(width=2)) +
#   geom_errorbar(data=plotData %>% filter(period != 2020, variable == vars[1], scenario %in%  c(mainScen,"Nzero_55_bio12")), aes(ymin=ribbon.min.total, ymax=ribbon.max.total), width=4, colour="black", alpha=0.9, linewidth=1,position = position_dodge(width=2)) +
#   # scale_y_continuous(labels = scales::percent, breaks = c(0,1,plotData[plotData$period == "2030",]$value,plotData[plotData$period == "2040",]$value,plotData[plotData$period == "2050",]$value)) +
#   coord_flip() +
#   facet_grid(bioLim~.) +
#   theme_doubleColumn() +
#   theme(panel.grid.minor.x = element_blank(),
#         panel.grid.major.y = element_blank()) +
#   #guides(y = "none") +
#   theme(axis.title.y=element_blank()) +
#   #theme(legend.position = "none") #+
#   scale_fill_manual(values = setNames(options$aesthetics$legend$color[names(vars)],vars), labels = setNames(names(vars), vars), guide = guide_legend(reverse = TRUE, nrow = 1)) +
#   scale_alpha_manual(values = c("2020"=0.7,"2030"=0.7,"2040"=1,"2050"=0.7), guide = 'none') +
#   theme(legend.text=element_text(size=theme.double.text.size)) +
#   theme(legend.key.height = unit(0.7, "cm"),
#     legend.key.width = unit(0.7,"cm")) +
#   scale_y_continuous(breaks = c(0,round(sum(plotData %>% filter(scenario == mainScen, period == 2020) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2030) %>% pull(value)),1),round(sum(plotData %>% filter(scenario == mainScen, period == 2040) %>% pull(value)),1))) +
#   #scale_x_reverse()
#   theme(legend.margin=margin(l = -2, unit='cm'))

@@

g[["Emissions reductions"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=0.55, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Emissions\nreductions", y = 0.55, label = "FitFor55", angle=90, vjust = -0.5, hjust = 1, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)

@@

g[["Energy savings"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=750, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Final Energy\nDemand", y = 787, label = "FitFor55", angle=90, vjust = 1.5, hjust = 1, color = "black", alpha = 0.5) +
  geom_hline(yintercept=787, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Final Energy\nDemand", y = 750, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.7, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(400,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(Mtoe)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.2, na.rm = TRUE)

# Electricity Demand
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "FE|Electricity") %>% select(-variable) %>%
  mutate(value = round(value * 1/0.0036)) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Electricity\nDemand") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

g[["Electricity Demand"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
  geom_hline(yintercept=2641, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Electricity\nDemand", y = 2641, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,5000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(TWh)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.2, na.rm = TRUE)

@@

g[["Renewables Share"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=0.4, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.4, label = "RED II revised", angle=90, vjust = -0.5, hjust = 0.5, color = "black", alpha = 0.5) +
  geom_hline(yintercept=0.45, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Renewables\nShare in\nFinal Energy", y = 0.45, label = "REPowerEU", angle=90, vjust = 1.5, hjust = 0.6, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  scale_y_continuous(breaks=seq(0, 1, 0.2), labels = scales::percent) +
  expand_limits(y=c(0,1)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(%)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.4, na.rm = TRUE)

# Wind
plotData <- df %>% filter(region == "EU27", period %in% c(2030,2040), tgt2030 %in% tgt2030Scen, variable == "Cap|Electricity|Wind") %>% select(-variable) %>%
  filter(tgt2050 != "Npi") %>%
  mutate(target = "Wind\ncapacity") %>%
  group_by(period) %>% 
  mutate(min = min(value),
        max = max(value))

#target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
g[["Wind capacity"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
  geom_hline(yintercept=255, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Wind\ncapacity", y = 255, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,1000)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.3, na.rm = TRUE)

@@

#target <- data.frame(target=c("REPowerEU","REPowerEU"),period=c(2025,2030),value=c(320,600)) 
g[["Solar photovoltaics"]] <- ggplot(plotData, aes(x = target, y = value, group=period)) +
  geom_errorbar(aes(ymin=min, ymax=max), width=0.3, colour="black", alpha=0.9, linewidth=1) +   
  geom_boxplot(outlier.shape = NA, width=0.6) +
         #stat_summary(geom = "text", fun = quantile,
        #              aes(label = paste0(round(..y..*100),"%")),
        #       #position=position_nudge(x=c(0.1,0.35,0.35,0.35,0.1)), 
         #      hjust=-1, angle = 90) +
  geom_hline(yintercept=600, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Solar\nphotovoltaics", y = 600, label = "REPowerEU", angle=90, vjust = -0.5, hjust = 0.6, color = "black", alpha = 0.5) +
  geom_hline(yintercept=208.9, color = "black", linewidth=1, alpha = 0.5, linetype = "dashed") +
  annotate("text", x = "Solar\nphotovoltaics", y = 208.9, label = "2022", angle=90, vjust = -0.5, hjust = 1.2, color = "black", alpha = 0.5) +
  facet_grid(target~period, scales="free") +
  theme_doubleColumn() +
  coord_flip(clip = 'off') +
  theme(axis.title.y=element_blank()) +
  theme(strip.text.y = element_blank()) +
  theme(strip.text.x = element_blank()) +
  expand_limits(y=c(0,2500)) + 
  theme(panel.spacing = unit(4, "lines")) +
  theme(axis.text.x = element_text(size = 0.8*theme.double.text.size)) +
  theme(axis.text.y = element_text(size = 1.2*theme.double.text.size)) +
  geom_text(data=data.frame(period=c(2030,2040),label=c("(GW)",NA)), aes(label = label,x = 0, y = 0), color = "#666666", size=0.8*geom.text.double.size, hjust=1.3, na.rm = TRUE)
